### 2025-09-24 paper/sec/authoring-workflow.tex

\item \textbf{Code synthesis step.} The expression synthesis step is an internal loop which starts with an
initial prompt sent to the LLM (\secref{prompt-design} below) requesting the generation of an expression $e$.
Using the Fluid command-line interface, the expression is validated to check that it evaluates without error,
produces a value coercible to a string $s'$, and finally that $s'$ is equal to the target fragment $s$. Any
failure triggers prompt augmentation with the appropriate error message and the system retries generation. If
code synthesis loop is able to yield an expression which computes $s$ within a maximum number of retries, the
synthesis step succeeds with $e$. If the last generated $e$ was invalid (resulting in an error), the code
synthesis step fails with no expression. Otherwise, code synthesis produces an expression $e$ but with a
mismatched string outcome $s' \neq s$.

>>>>

\item \textbf{Code synthesis step.} The expression synthesis step is an error-guided iterative prompting
loop~\citep{skreta23}, beginning with an initial prompt sent to the LLM (\secref{prompt-design} below)
requesting the generation of an expression $e$. Using the Fluid command-line interface, the expression is
validated to check that it evaluates without error, produces a value coercible to a string $s'$, and finally
that $s'$ is equal to the target fragment $s$. Any failure triggers prompt augmentation with the appropriate
error message and the system retries generation. If code synthesis loop is able to yield an expression which
computes $s$ within a maximum number of retries, the synthesis step succeeds with $e$. If the last generated
$e$ was invalid (resulting in an error), the code synthesis step fails with no expression. Otherwise, code
synthesis produces an expression $e$ but with a mismatched string outcome $s' \neq s$.
